---
title: "Danish Kings and Animation"
author: "Marie Johannsen"
date: "03-10-2023"
---

### Setting up
##### Firstly, I ran the tidyverse and here packages on my RMarkdown document and created the vector Full_data_kings with the data from my spreadsheet of the kings.
```{r setup, echo=TRUE, message=FALSE}
library(tidyverse)
library(here)
Full_data_kings <- read_csv("data/Konger.csv")
```

### Finding the duration of reign
##### Secondly, I mutated the data to create a new column with the duration of reign by subtracting the start-reign-data from the end-reign-data and this gave me a new column, which I named duration_reign.
```{r new column, include=TRUE}
Full_data_kings %>% 
  mutate(duration_reign = `End reign`- `Start reign`) %>% 
  glimpse()
```
##### Next, I made the duration_reign data into its own vector called reign.
```{r new vector, include=TRUE}
reign <- Full_data_kings %>% 
  mutate(duration_reign = `End reign`- `Start reign`)
```

### Visualization
##### Lastly, I created my visualization of the reign-vector using ggplot. I chose the specifics for my graph as seen below, the name "Time" for the x-axis and "Duration of reign" for the y-axis and the colour blue. For my x-axis I used the start-reign data to base it on, because it gives me a progressing timeline matching the other data and I wouldnt know how to create a custom timeline in R in an easy way. 
```{r visualization, include=TRUE, warning=FALSE}

reign %>% 
  ggplot(aes(x = `Start reign`, y = duration_reign))+
  geom_line (color="blue")+
  geom_jitter()+
  labs (x = "Time",
        y = "Duration of reign")+
  theme_get()
```

